Association between trauma severity models and opportunities for improvement:

### 2022-10-26 manuscript.Rmd
added text about UN sdg

Introduction
============
Trauma, defined as the clinical entity composed of physical injury and the body's associated response [@Gerdin2015], is one of the leading causes of death worldwide, constituting nearly 8% of global deaths annually [@globalburden]. The global health burden of trauma has led to it being described as a worldwide pandemic. One of the characteristics of this particular pandemic is its demographic spread; trauma is a leading cause of death for people aged 10-49 years [@globalburden] and 90% of trauma-related deaths occur in low- to middle-income countries [@whoepi]. Non-fatal outcomes also comprise a significant portion of the global health burden of disability [@globalburden], which can drastically reduce quality of life and health status in survivors of severe trauma [@globalburden; @longtermtrauma]. Improvements in trauma outcomes stand therefore to benefit a broader population by reducing the societal and healthcare costs of disability, not least in low- and middle-income countries.

<!-- S wants me to write about the UN 2030 goals here -->

@@

```{r, echo = FALSE}
plot(t.stats[['perf']], main="Fig 3. TRISS Receiver Operating Characteristic Curve.", colorize = TRUE)
```

@@

```{r, echo = FALSE}
plot(n.stats[['perf']], main="Fig 5. NORMIT Receiver Operating Characteristic Curve.", colorize = TRUE)
```

@@

<!--

Key results
-----------
Summarise key results with reference to study objectives

@@

Discuss limitations of the study, taking into account sources of
potential bias or imprecision.  Discuss both direction and magnitude
of any potential bias

Interpretation
--------------

>>>>

Introduction
============
Trauma, defined as the clinical entity composed of physical injury and the body's associated response [@Gerdin2015], is one of the leading causes of death worldwide, constituting around 9% of global deaths annually [@globalburden]. The global health burden of trauma has led to it being described as a worldwide pandemic. One of the characteristics of this particular pandemic is its demographic spread; trauma is a leading cause of death for people aged 10-49 years [@globalburden] and 90% of trauma-related deaths occur in low- to middle-income countries [@whoepi]. Non-fatal outcomes also comprise a significant portion of the global health burden of disability [@globalburden], which can drastically reduce quality of life and health status in survivors of severe trauma [@globalburden; @longtermtrauma]. The UN's Sustainable Development Goals, published in 2015, included the aim of reducing the number of global deaths and injuries from road traffic accidents by half by 2020 <!-- [@spg] -->. This goal was not met, as global mortality from road traffic accidents was only reduced by 8.3% from 2010 to 2019 <!-- [@spg2020] -->. Improvements in trauma outcomes stand therefore to benefit a broader population by reducing the societal and healthcare costs of disability, not least in low- and middle-income countries.

@@

```{r, echo = FALSE}
plot(t.stats[['roc']], main="Fig 3. TRISS Receiver Operating Characteristic Curve.", colorize = TRUE)
```

@@

```{r, echo = FALSE}
plot(n.stats[['roc']], main="Fig 5. NORMIT Receiver Operating Characteristic Curve.", colorize = TRUE)
```

@@

<!-- 
Key results
-----------
Summarise key results with reference to study objectives

@@

<!-- 
Discuss limitations of the study, taking into account sources of
potential bias or imprecision.  Discuss both direction and magnitude
of any potential bias -->

<!-- 
Interpretation
--------------
